The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-06-08 Paper.Rmd
minor change

The model-averaged (AIC weights used for model averaging) lower-tail and upper-tail dependence statistic was `r BivMS_BMR$relLTdep_AICw - BivMS_BMR$relUTdep_AICw`, indicating nearly symmetric tail dependence. BB1, being as a two parameter copula,  has both lower and upper tail dependence and depending upon which parameter is greater it shows comparatively greater lower or upper tail dependence. SBB1 is just opposite of BB1 in tail dependency. So, the result was expected, because the contributions came from more or less equally weighted BB1 and SBB1. We also tested that lowest-AIC copula BB1 was a good-enough fit, giving $p$-value `r BivMS_BMR$GofRes_CvM` (to within the precision available from `BiCopGofTest` in the `VineCopula` package) in the Cramer-von Mises-based test of the goodness of its fit, and $p$-value `r BivMS_BMR$GofRes_KS` in the Kolmogorov-Smirnov-based test of the goodness of fit. The next section looks at tail dependence in a non-parametric way.

@@

Results indicate that dependence of data is different in some bins than would be expected under a 
null hypothesis of a normal copula, answering the second part of question 1. But Table \ref{SM-tab_BMR_asym} indicates that tail dependence for the BMR data copula is significantly (95% CI) not different from symmetric normal copula and thus consistent with model selection results.

>>>>

The model-averaged (AIC weights used for model averaging) lower-tail and upper-tail dependence statistic was `r BivMS_BMR$relLTdep_AICw - BivMS_BMR$relUTdep_AICw`, indicating nearly symmetric tail dependence. BB1, being as a two parameter copula,  has both lower and upper tail dependence and depending upon which parameter is greater it shows comparatively greater lower or upper tail dependence. SBB1 is just opposite of BB1 in tail dependency. So, the result was expected, because the contributions came from more or less equally weighted BB1 and SBB1 with nearly same tail dependencies. We also tested that lowest-AIC copula BB1 was a good-enough fit, giving $p$-value `r BivMS_BMR$GofRes_CvM` (to within the precision available from `BiCopGofTest` in the `VineCopula` package) in the Cramer-von Mises-based test of the goodness of its fit, and $p$-value `r BivMS_BMR$GofRes_KS` in the Kolmogorov-Smirnov-based test of the goodness of fit. The next section looks at tail dependence in a non-parametric way.

@@

Results indicate that dependence of data is different in some bins than would be expected under a 
null hypothesis of a normal copula, answering the second part of question 1. But Table \ref{SM-tab_BMR_asym} indicates that difference in tail dependence for the BMR data copula is significantly (95% CI) not different from that of the symmetric normal copula and thus consistent with model selection results.
